Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society

### 2024-02-24 manuscript/manuscript.qmd
Switch to JSON-based references for better APA capitalization

  **Conflict of Interest:** The authors declare that they have no conflict of interest.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
word-count: "7,984"
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.bib
link-citations: true
toc-depth: 4
---

>>>>

  **Conflict of Interest:** The authors declare that they have no conflict of interest.
keywords:
  - international NGOs
  - civil society
  - authoritarianism
  - Chinese ONGO law
word-count: "7,984"
code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/compassionate-clam>"
bibliography: references.json
link-citations: true
toc-depth: 4
---
